### 2011-04-23 docs/architecture/architecture.tex
rework the description of a box

The routines in {\tt MAESTRO/initial\_model/} prepare an initial model
for MAESTRO.  There are two types of routines here, the first type
take an existing 1-d initial model produced somewhere else (e.g.\ a
1-d stellar evolution code), and and map it onto a uniform grid, at
the desired resolution, using the equation of state in MAESTRO, and
using MAESTRO's discretization of hydrostatic equilibrium.  The second
type generate the initial model internally, by integrating the
condition of hydrostatic equilibrium together with a simplifying
assumption on the energy (e.g. isothermal or isentropic).  In
both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}

@@

MAESTRO's gridding is handled by the BoxLib library.  The underlying
idea in BoxLib is to allow for adaptive mesh refinement (AMR)---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

A \boxtype\ is simply a rectangular domain in space.  Note that boxes
do not hold the state data themselves.  The datatype for a
\boxtype\ is
\begin{verbatim}
  type box
     integer :: dim  = 0
     integer :: lo(MAX_SPACEDIM) =  Huge(1)
     integer :: hi(MAX_SPACEDIM) = -Huge(1)
  end type box
\end{verbatim}

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt lo} is the index of the lower bound of the box
\item {\tt hi} is the index of the upper bound of the box
\end{itemize}

@@

The computational domain is divided into boxes.  The collection of
boxes with the same resolution comprise a level.
Figure~\ref{fig:boxes} shows three boxes in the same level of
refinement.  The position of the boxes is with respect to a global
index space at that level.  For example, box 1 in the figure has {\tt
  lo} = (3,7) and {\tt hi} = (9,12).

>>>>

The routines in {\tt MAESTRO/initial\_model/} prepare an initial model
for MAESTRO.  There are two types of routines here, the first type
take an existing 1-d initial model produced somewhere else (e.g.\ a
1-d stellar evolution code), and and map it onto a uniform grid, at
the desired resolution, using the equation of state in MAESTRO, and
using MAESTRO's discretization of hydrostatic equilibrium.  The second
type generate the initial model internally, by integrating the
condition of hydrostatic equilibrium together with a simplifying
assumption on the energy (e.g. isothermal or isentropic).  In
both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}
Here, $g_{i+1/2}$ is the edge-centered gravitational acceleration.

@@

MAESTRO's gridding is handled by the BoxLib library.  The underlying
idea in BoxLib is to allow for adaptive mesh refinement (AMR)---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.

\MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

A \boxtype\ is simply a rectangular domain in space.  Note that boxes
do not hold the state data themselves.  A \boxtype\ has a {\tt lo} 
and {\tt hi} index in each coordinate direction that gives the
location of the lower-left and upper-right corner with respect to
a global index space.

@@

The computational domain is divided into boxes.  The collection of
boxes with the same resolution comprise a level.
Figure~\ref{fig:boxes} shows three boxes in the same level of
refinement.  The position of the boxes is with respect to the global
index space at that level.  For example, box 1 in the figure has {\tt
  lo} = (3,7) and {\tt hi} = (9,12).  Note that the global indexing
is 0-based.

The global index space covers the entire domain at a given resolution.
For a simulation setup with {\tt n\_cellx = 32} and {\tt n\_celly =
  32}, the coarsest level (level 1) has $32 \times 32$ zones, and the
global index space will run from $0, \ldots, 31$ in each coordinate
direction.  Level 2 will have a global index space running from $0,
\ldots, 63$ in each coordinate direction (corresponding to $64 \times
64$ zones if fully refined), and level 3 will have a global index
space running from $0, \ldots, 127$ in each coordinate direction
(corresponding to $128\times 128$ zones if fully refined).
